The Birth of a Galaxy: Population III Metal Enrichment and Population II Stellar Populations

### 2010-10-27 science_ms.tex
Adding DLA and z=8.6 galaxy references.

Numerical simulations are useful to detangle and study these
complexities and the transition from Pop III to II stars.  In this
Report, we present the simulations that include both types of SF, and
their radiative and mechanical feedback.  The methods used here
incorporate and link together recent results from metal-enriched and
metal-free star formation, the critical metallicity, and
pair-instability supernovae.  This is the first simulation that can
resolve star-forming minihalos while following the transition to Pop
II star formation in the first galaxies.

@@

@@

We find that one PISN is sufficient to enrich the star-forming halo
and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
on the same order \cite{DLAs}, and metal enrichment from Pop III SNe
provides a possible explaination.

>>>>

Numerical simulations are useful to detangle and study these
complexities and the transition from Pop III to II stars.  In this
Report, we present the simulations that include both types of SF, and
their radiative and mechanical feedback.  The methods used here
incorporate and link together recent results from metal-enriched and
metal-free star formation, the critical metallicity, and
pair-instability supernovae.  This is the first time it has been
possible to link the formation and feedback of the first stars to
protogalaxies resolving the important scales and including the most
important physical effects.

@@

\textbf{Add some interesting stats about the simulation.}

@@

We find that one PISN is sufficient to enrich the star-forming halo
and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
on the same order \cite{Wolfe05_Review}, and metal enrichment from Pop
III SNe provides a possible explanation.
